---
title: "Dengue Data Hub: "
subtitle: "A Centralized Repository for Dengue-related Data"  
author: 
  - "Thiyanga S. Talagala"
  - "University of Sri Jayewardenepura, Sri Lanka"
date: 'R/Medicine Conference 2023 '
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{css, echo = FALSE}
h1, #TOC>ul>li {
  color: #3f007d;
  font-weight: bold;
}
h2, #TOC>ul>ul>li {
  color:  #3f007d;
  #font-family:  "Times";
  font-weight: bold;
}
h3, #TOC>ul>ul>li {
  color: #ce1256;
  #font-family:  "Times";
  font-weight: bold;
}
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF",
  title_slide_background_color = "#051454",
  title_slide_text_color = "#f5ef4c"
)
```

<style type="text/css">
.remark-slide-content {
    font-size: 30px;
    padding: 1em 4em 1em 4em;
}
</style>

## What is Dengue?

- Viral infection caused by the dengue virus (DENV), transmitted to humans through the bite of infected mosquitoes

---
## Prevalent in the tropical regions of the world

---

## About half of the world's population is now at risk of dengue 

---

# Small bite -Big threat!

---

# Small bite - Big threat!

# Small data - Big impact!


---

## Outline

- Why?

- Where?

- To whom?

- What do we have?

- How to use?

---

## Outline

- **Why?**

- Where?

- To whom?

- What do we have?

- How to use?
- How to collaborate?


---

## Data Analysis Workflow

---

## Dengue Data Hub

---

## To whom

- Epidemiologists

- Researchers

- Educators

